---
title: "PSYC573 Final"
author: "Sherry Zhang"
date: "4/17/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-pkg, message = FALSE, warning=FALSE}
library(ggplot2)  # for plots
library(magrittr)  # for `%>%` operator
library(here)
library(readxl)  # for reading excel files
library(modelsummary)  # for summarizing data
library(rstan)
rstan_options(auto_write = TRUE)  # save compiled STAN object
library(posterior)
library(bayesplot)
library(brms)
library(dplyr)
library(splines)
```


## Research Question
Does the type and polarity of a distractor (mask) affect recognition of a target letter when flashed quickly across a monitor?

## Description of each variable in your preliminary analysis

Contrast: The brightness of the mask, compared to the letters. Ranges from twice as bright to .2 times as bright as the letters. Light-colored masks are on the negative scale, while dark-colored masks were on the positive scale.

Mask type:
1-strip of masking (covers a small portion of the monitor) that does not overlap with the target
0-full field (covers entire monitor) of masking that overlaps with target

Accuracy: Overall accuracy across subjects for each condition.

## Mathematical expressions of your model and priors
Let $C$ = contrast, $M$ = Mask Type

Model:
$$
  \begin{aligned}
    A_i & \sim N(\mu_i, \sigma) \\
    \mu_i & = \beta_0+\beta_1C_i+\beta_2M_i+\beta_3C_i\times M_i
  \end{aligned}
$$

Prior:
$$
  \begin{aligned}
    \beta_0 & \sim N(0, 5) \\
    \beta_1 & \sim N(0, 5) \\
    \beta_2 & \sim N(0, 1) \\
    \beta_3 & \sim N(0, 2) \\
    \sigma & \sim t_4^+(0, 3) \\
    X & \sim I(abs(C))
  \end{aligned}
$$

##Your code for running the Bayesian analyses
```{r}
#reading in data
hw9 <- read_excel(file.choose())
```

```{r}
hw9$mask <- factor(hw9$mask,
    levels = c(1, 0),
    labels = c("strip", "fullfield")
)
```

Models for different mask types:
```{r, results = "hide"}
m_strip <-
    brm(accuracy ~ contrast,
        data = filter(hw9, mask == "strip"),
        prior = prior(normal(0, 5), class = "b") +
            prior(normal(0, 1), class = "Intercept") +
            prior(student_t(4, 0, 3), class = "sigma"),
        seed = 941,
        iter = 4000
    )
m_fullfield <-
    brm(accuracy ~ contrast,
        data = filter(hw9, mask == "fullfield"),
        prior = prior(normal(0, 5), class = "b") +
            prior(normal(0, 2), class = "Intercept") +
            prior(student_t(4, 0, 3), class = "sigma"),
        seed = 2157,
        iter = 4000
    )
```

```{r}
msummary(list(mask = m_strip, `fullfield` = m_fullfield),
         estimate = "{estimate} [{conf.low}, {conf.high}]",
         statistic = NULL, fmt = 2,
         gof_omit = "^(?!Num)"
)
```

Interaction model:
```{r}
get_prior(accuracy ~ contrast + mask,
    data = hw9,
    family = gaussian(link = "identity"))
get_prior(accuracy ~ contrast,
    data = hw9,
    family = gaussian(link = "identity"))
```

```{r, results = "hide"}
m_int <- brm(
    accuracy ~ mask + bs(contrast, degree = 1, knots = 0),
    data = hw9,
    prior = 
        prior(student_t(3, 0.6, 2.5), class = "Intercept") +
        prior(student_t(3, 0, 2.5), class = "sigma"),
    seed = 941,
    iter = 4000
)
```

```{r}
m_int
```

##A convergence check of MCMC
```{r}
mcmc_trace(m_int)
summarize_draws(m_int)
```

##A table and/or a figure showing the posterior distributions of the key model parameters

```{r summ-m1}
summ_m_int <- as_draws_df(m_int) %>%
    summarise_draws()
knitr::kable(summ_m_int, digits = 2)
```

```{r}
plot(
    conditional_effects(m_int),
    points = TRUE,
    point_args = list(height = 0.01, width = 0.05, alpha = 0.05)
)
```

```{r}
ggplot(hw9,
       aes(x = contrast, y = accuracy, col = mask)) +
    geom_point() +
    geom_smooth() +
    labs(x = "Relative Contrast",
         y = "Accuracy",
         title = "Stratified Analysis of Mask Type and Accuracy")
```

```{r}
pp_check(m_int, type = "dens_overlay_grouped", group = "mask")
```
